Foreground Detection via Deep Variation Transformation

### 2018-12-02 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex

%me
\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
\label{sec4}
In this section, we will introduce the details of proposed approaches. 
We explain the production of the pixel patch, which is a specific form of the pixel variation, and the architecture of our network.

The flow chart of the proposed approach is illustrated in \reffig{flow_chart}. 
Firstly, we sample the input and ground truth images to generalize the pixel variations, and reshape them into patches and feed them into the network with its spatial neighbors. 
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
    \label{flow_chart}
\end{figure*}

% 第一步是对原视频进行采样
Given different videos, their numbers of frames are generally different. 
In order to keep each piece of variation the same length, image stacks are sampled from the given videos before the pixel variations are extracted. 
Let denote the frames sequence as:
\begin{equation}
    \mathcal{I} = \{I_1, I_2, \cdots, I_T\}, \\\\
\end{equation}

And image stacks can be defined as follows: 
\begin{equation}
    \mathcal{I}^d = \mathcal{D}(\mathcal{I})=  \{I_1, I_{[2 \cdot \frac{T}{N}]}, \cdots, I_{[(N - 1) \cdot \frac{T}{N}]}, \}
\end{equation}
% 解释采样的细节
where $I_t$ is the frame $t$ of the given video. 
$T$ and $N$ represent respectively the totall number of the video frames and the number of image stacks. 
For each video, we can produce multiple image stacks and choose one of them for the training. 
In addition, we can get compact pixel variations, which contain more temporal information than the continuous pixel sequences, by using equal interval sampling.

>>>>

%me
\section{Foreground Detection via Deep Variation Transformation}
\label{sec4}
In this section, the details of proposed approach is explained.
%
The flow chart of the proposed approach is illustrated in \reffig{flow_chart}.
%
We firstly introduce the procedure of generating pixels patch,
which is feed into the network as well as the description of pixel variation.
%
Then,
the architecture of the network, which is used for variation transformation, is explained.
%
%We explain the production of the pixel patch, 
%which is a specific form of the pixel variation, and the architecture of our network. 
%

\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{ Original videos break down into pixel patches for the training of the FCN, which 
Fully convolutional network produces an efficient machine for end-to-end transformation learning.}
    \label{flow_chart}
\end{figure*}
% Firstly, we sample the input and ground truth images to generalize the pixel variations, 
% and reshape them into patches and feed them into the network with its spatial neighbors. 
% %
% After reassembling the patches into the complete output frame, 
% it is post-processed, yielding the final segmentation of the respective video frame.

% 第一步是对原视频进行采样
There are usually large numbers of frames in a particular video.
%
In order to capture the global representation of pixel's variation,
the training frames are sampled from the whole frame sequenece uniformly.
%
Let us denote the frame sequence as $\mathcal{I} = \{I_1, I_2, \cdots, I_T\}$,
where $\mathcal{I}$ is denoted as the set of frames and $T$ is the numbers of frames.
%
The uniform sampling procedure is shown as follows:
% 
% Given different videos, their numbers of frames are generally different. 
% In order to keep each piece of variation the same length,
% image stacks are sampled from the given videos before the pixel variations are extracted. 
% Let denote the frames sequence as:
% \begin{equation}
%     \mathcal{I} = \{I_1, I_2, \cdots, I_T\}, \\\\
% \end{equation}
% 
% And image stacks can be defined as follows: 
\begin{equation}
    \mathcal{I}^d = \mathcal{D}(\mathcal{I})=  \{I_1, I_{[2 \cdot \frac{T}{N}]}, \cdots, I_{[(N - 1) \cdot \frac{T}{N}]}, \}
\end{equation}
where $\mathcal{I}^d$ is the set of training frames,
the $T$ and the $N$ represents the frame number of whole video and the training set respectively,
and the $\mathcal{D}()$ is denoted as the sampling function.

%

% 解释采样的细节
where $I_t$ is the frame $t$ of the given video. 
$T$ and $N$ represent respectively the totall number of the video frames and the number of image stacks. 
For each video, we can produce multiple image stacks and choose one of them for the training. 
In addition, we can get compact pixel variations, which contain more temporal information than the continuous pixel sequences, by using equal interval sampling.
